イーサリアム: 安全な分散型汎用トランザクション台帳\\ \smaller \textbf{{Berlin version \YellowPaperVersionNumber}}

### 2022-07-19 Paper.tex
[WIP] add-paragraph

\begin{abstract}
    ブロックチェーンパラダイムは、暗号化された安全な取引と結びついたとき、多くのプロジェクトを通じてその有用性を実証しており、ビットコインは最も注目すべきものの1つです。
    このようなプロジェクトは、分散型だがシングルトンの計算資源上の単純なアプリケーションと見なすことができる。
    このパラダイムを、共有された状態(shared-state)を持つトランザクショナル・シングルトン・マシンと呼ぶことができる。

    Ethereumはこのパラダイムを一般化した形で実装しています。さらに、このようなリソースを複数用意し、それぞれが個別の状態と操作コードを持つが、メッセージパッシングのフレームワークを通じて他のリソースと相互作用することが可能である。

    本稿では、イーサリアムの設計、実装上の問題点、提供される機会、そして我々が想定する将来のハードルについて議論する。
\end{abstract}

@@

With ubiquitous internet connections in most places of the world, global information transmission has become incredibly cheap. Technology-rooted movements like Bitcoin have demonstrated through the power of the default, consensus mechanisms, and voluntary respect of the social contract, that it is possible to use the internet to make a decentralised value-transfer system that can be shared across the world and virtually free to use. This system can be said to be a very specialised version of a cryptographically secure, transaction-based state machine. Follow-up systems such as Namecoin adapted this original ``currency application'' of the technology into other applications albeit rather simplistic ones.

Ethereum is a project which attempts to build the generalised technology; technology on which all transaction-based state machine concepts may be built. Moreover it aims to provide to the end-developer a tightly integrated end-to-end system for building software on a hitherto unexplored compute paradigm in the mainstream: a trustful object messaging compute framework.

@@

There are many goals of this project; one key goal is to facilitate transactions between consenting individuals who would otherwise have no means to trust one another. This may be due to geographical separation, interfacing difficulty, or perhaps the incompatibility, incompetence, unwillingness, expense, uncertainty, inconvenience, or corruption of existing legal systems. By specifying a state-change system through a rich and unambiguous language, and furthermore architecting a system such that we can reasonably expect that an agreement will be thus enforced autonomously, we can provide a means to this end.

Dealings in this proposed system would have several attributes not often found in the real world. The incorruptibility of judgement, often difficult to find, comes naturally from a disinterested algorithmic interpreter. Transparency, or being able to see exactly how a state or judgement came about through the transaction log and rules or instructional codes, never happens perfectly in human-based systems since natural language is necessarily vague, information is often lacking, and plain old prejudices are difficult to shake.

Overall, we wish to provide a system such that users can be guaranteed that no matter with which other individuals, systems or organisations they interact, they can do so with absolute confidence in the possible outcomes and how those outcomes might come about.

@@

\cite{buterin2013ethereum} first proposed the kernel of this work in late November, 2013. Though now evolved in many ways, the key functionality of a block-chain with a Turing-complete language and an effectively unlimited inter-transaction storage capability remains unchanged.

\cite{dwork92pricingvia} provided the first work into the usage of a cryptographic proof of computational expenditure (``proof-of-work'') as a means of transmitting a value signal over the Internet. The value-signal was utilised here as a spam deterrence mechanism rather than any kind of currency, but critically demonstrated the potential for a basic data channel to carry a \textit{strong economic signal}, allowing a receiver to make a physical assertion without having to rely upon \textit{trust}. \cite{back2002hashcash} later produced a system in a similar vein.

The first example of utilising the proof-of-work as a strong economic signal to secure a currency was by \cite{vishnumurthy03karma:a}. In this instance, the token was used to keep peer-to-peer file trading in check, providing ``consumers'' with the ability to make micro-payments to ``suppliers'' for their services. The security model afforded by the proof-of-work was augmented with digital signatures and a ledger in order to ensure that the historical record couldn't be corrupted and that malicious actors could not spoof payment or unjustly complain about service delivery. Five years later, \cite{nakamoto2008bitcoin} introduced another such proof-of-work-secured value token, somewhat wider in scope. The fruits of this project, Bitcoin, became the first widely adopted global decentralised transaction ledger.

Other projects built on Bitcoin's success; the alt-coins introduced numerous other currencies through alteration to the protocol. Some of the best known are Litecoin and Primecoin, discussed by \cite{sprankel2013technical}. Other projects sought to take the core value content mechanism of the protocol and repurpose it; \cite{aron2012bitcoin} discusses, for example, the Namecoin project which aims to provide a decentralised name-resolution system.

Other projects still aim to build upon the Bitcoin network itself, leveraging the large amount of value placed in the system and the vast amount of computation that goes into the consensus mechanism. The Mastercoin project, first proposed by \cite{mastercoin2013willett}, aims to build a richer protocol involving many additional high-level features on top of the Bitcoin protocol through utilisation of a number of auxiliary parts to the core protocol. The Coloured Coins project, proposed by \cite{colouredcoins2012rosenfeld}, takes a similar but more simplified strategy, embellishing the rules of a transaction in order to break the fungibility of Bitcoin's base currency and allow the creation and tracking of tokens through a special ``chroma-wallet''-protocol-aware piece of software.

Additional work has been done in the area with discarding the decentralisation foundation; Ripple, discussed by \cite{boutellier2014pirates}, has sought to create a ``federated'' system for currency exchange, effectively creating a new financial clearing system. It has demonstrated that high efficiency gains can be made if the decentralisation premise is discarded.

Early work on smart contracts has been done by \cite{szabo1997formalizing} and \cite{miller1997future}. Around the 1990s it became clear that algorithmic enforcement of agreements could become a significant force in human cooperation. Though no specific system was proposed to implement such a system, it was proposed that the future of law would be heavily affected by such systems. In this light, Ethereum may be seen as a general implementation of such a \textit{crypto-law} system.

%E language?
For a list of terms used in this paper, refer to Appendix~\ref{ch:Terminology}.

\section{The Blockchain Paradigm} \label{ch:overview}

Ethereum, taken as a whole, can be viewed as a transaction-based state machine: we begin with a genesis state and incrementally execute transactions to morph it into some current state. It is this current state which we accept as the canonical ``version'' of the world of Ethereum. The state can include such information as account balances, reputations, trust arrangements, data pertaining to information of the physical world; in short, anything that can currently be represented by a computer is admissible. Transactions thus represent a valid arc between two states; the `valid' part is important---there exist far more invalid state changes than valid state changes. Invalid state changes might, \eg, be things such as reducing an account balance without an equal and opposite increase elsewhere. A valid state transition is one which comes about through a transaction. Formally:
\begin{equation}
\linkdest{Upsilon_state_transition}\linkdest{Upsilon}\boldsymbol{\sigma}_{t+1} \equiv \Upsilon(\boldsymbol{\sigma}_{t}, T)
\end{equation}

where $\Upsilon$ is the Ethereum state transition function. In Ethereum, $\Upsilon$, together with $\boldsymbol{\sigma}$ are considerably more powerful than any existing comparable system; $\Upsilon$ allows components to carry out arbitrary computation, while $\boldsymbol{\sigma}$ allows components to store arbitrary state between transactions.

Transactions are collated into blocks; blocks are chained together using a cryptographic hash as a means of reference. Blocks function as a journal, recording a series of transactions together with the previous block and an identifier for the final state (though do not store the final state itself---that would be far too big). They also punctuate the transaction series with incentives for nodes to \textit{mine}. This incentivisation takes place as a state-transition function, adding value to a nominated account.

Mining is the process of dedicating effort (working) to bolster one series of transactions (a block) over any other potential competitor block. It is achieved thanks to a cryptographically secure proof. This scheme is known as a proof-of-work and is discussed in detail in section \ref{ch:pow}.

Formally, we expand to:
\begin{eqnarray}
\boldsymbol{\sigma}_{t+1} & \equiv & \hyperlink{Pi}{\Pi}(\boldsymbol{\sigma}_{t}, B) \\
B & \equiv & (..., (T_0, T_1, ...), ...) \\
\Pi(\boldsymbol{\sigma}, B) & \equiv & \hyperlink{Omega}{\Omega}(B, \hyperlink{Upsilon}{\Upsilon}(\Upsilon(\boldsymbol{\sigma}, T_0), T_1) ...)
\end{eqnarray}

>>>>

\begin{abstract}
The blockchain paradigm when coupled with cryptographically-secured transactions has demonstrated its utility through a number of projects, with Bitcoin being one of the most notable ones. Each such project can be seen as a simple application on a decentralised, but singleton, compute resource. We can call this paradigm a transactional singleton machine with shared-state.

Ethereum implements this paradigm in a generalised manner. Furthermore it provides a plurality of such resources, each with a distinct state and operating code but able to interact through a message-passing framework with others. We discuss its design, implementation issues, the opportunities it provides and the future hurdles we envisage.
\end{abstract}

@@

世界中のほとんどの場所でインターネットに接続できるようになり、グローバルな情報発信が驚くほど安価にできるようになりました。

ビットコインのような技術に根ざした動きは、デフォルトの力、コンセンサスメカニズム、社会契約の自発的な尊重を通じて、インターネット　を使って、世界中で共有でき、事実上無料で使える分散型の価値伝達システムを作ることが可能であることを実証した。

このシステムは、暗号学的に安全な、トランザクションベースのステートマシンの非常に特殊なバージョンであると言うことができる。

その後、Namecoinのようなシステムが、この当初の「通貨アプリケーション」の技術をかなり単純なものではあるが、他の用途に応用している。

イーサリアムは、すべてのトランザクションベースのステートマシンの概念を構築することができる汎用的な技術を構築しようとするプロジェクトである。

さらに、信頼性の高いオブジェクトメッセージング・コンピューティングフレームワークという、これまで主流ではなかったコンピューティングパラダイムでソフトウェアを構築するための、緊密に統合されたエンドツーエンドシステムをエンド開発者に提供することを目的としています。

@@

このプロジェクトにはさまざまな目的がありますが、重要な目的のひとつは、互いに**信頼する術を持たない、**同意した個人間の取引を円滑にすることです。

これは、地理的な隔たり、インターフェースの難しさ、あるいは既存の法体系の非互換性、無能力、不本意、費用、不確実性、不便、腐敗などが原因かもしれません。

豊かで曖昧さのない言語によって状態変化システムを指定し、さらに、合意が自律的に執行されることを合理的に期待できるようなシステムを構築することによって、この目的のための手段を提供することができる。

この提案されたシステムでの取引は、現実世界ではあまり見られないいくつかの属性を持つことになる。判断の無節操さは，しばしば見つけるのが難しいが，利害関係のないアルゴリズム解釈者から自然に得られる．透明性、つまりある状態や判断がどのようにして生じたかをトランザクションログやルールや命令コードを通して正確に見ることができることは、人間ベースのシステムでは決して完璧には起こりえないことである
自然言語は曖昧であり、情報は不足しがちであり、また古くからの偏見も拭い去れないからである。

全体として、私たちは、ユーザーが他のどの個人、システム、組織とやりとりする場合でも、次のようなことが保証されるようなシステムを提供したいと願っています。
可能な結果と、その結果がどのようにもたらされるかについて、絶対的な確信を持って行うことができるようなシステムを提供したいと考えています。

@@

% \cite{buterin2013ethereum} は、2013年11月末にこの研究のカーネルを初めて提案しました。現在では多くの点で進化していますが、チューリング完全言語と事実上無制限のトランザクション間保存能力を持つブロックチェーンの主要な機能は変わっていません。

% \cite{dwork92pricingvia} provided the first work into the usage of a cryptographic proof of computational expenditure (``proof-of-work'') as a means of transmitting a value signal over the Internet. The value-signal was utilised here as a spam deterrence mechanism rather than any kind of currency, but critically demonstrated the potential for a basic data channel to carry a \textit{strong economic signal}, allowing a receiver to make a physical assertion without having to rely upon \textit{trust}. \cite{back2002hashcash} later produced a system in a similar vein.
% DworkとNaor[1992]は、計算の暗号学的証明の使用に関する最初の研究を提供しました。

% The first example of utilising the proof-of-work as a strong economic signal to secure a currency was by \cite{vishnumurthy03karma:a}. In this instance, the token was used to keep peer-to-peer file trading in check, providing ``consumers'' with the ability to make micro-payments to ``suppliers'' for their services. The security model afforded by the proof-of-work was augmented with digital signatures and a ledger in order to ensure that the historical record couldn't be corrupted and that malicious actors could not spoof payment or unjustly complain about service delivery. Five years later, \cite{nakamoto2008bitcoin} introduced another such proof-of-work-secured value token, somewhat wider in scope. The fruits of this project, Bitcoin, became the first widely adopted global decentralised transaction ledger.

% Other projects built on Bitcoin's success; the alt-coins introduced numerous other currencies through alteration to the protocol. Some of the best known are Litecoin and Primecoin, discussed by \cite{sprankel2013technical}. Other projects sought to take the core value content mechanism of the protocol and repurpose it; \cite{aron2012bitcoin} discusses, for example, the Namecoin project which aims to provide a decentralised name-resolution system.

% Other projects still aim to build upon the Bitcoin network itself, leveraging the large amount of value placed in the system and the vast amount of computation that goes into the consensus mechanism. The Mastercoin project, first proposed by \cite{mastercoin2013willett}, aims to build a richer protocol involving many additional high-level features on top of the Bitcoin protocol through utilisation of a number of auxiliary parts to the core protocol. The Coloured Coins project, proposed by \cite{colouredcoins2012rosenfeld}, takes a similar but more simplified strategy, embellishing the rules of a transaction in order to break the fungibility of Bitcoin's base currency and allow the creation and tracking of tokens through a special ``chroma-wallet''-protocol-aware piece of software.

% Additional work has been done in the area with discarding the decentralisation foundation; Ripple, discussed by \cite{boutellier2014pirates}, has sought to create a ``federated'' system for currency exchange, effectively creating a new financial clearing system. It has demonstrated that high efficiency gains can be made if the decentralisation premise is discarded.

% Early work on smart contracts has been done by \cite{szabo1997formalizing} and \cite{miller1997future}. Around the 1990s it became clear that algorithmic enforcement of agreements could become a significant force in human cooperation. Though no specific system was proposed to implement such a system, it was proposed that the future of law would be heavily affected by such systems. In this light, Ethereum may be seen as a general implementation of such a \textit{crypto-law} system.

% %E language?
% For a list of terms used in this paper, refer to Appendix~\ref{ch:Terminology}.

% \section{The Blockchain Paradigm} \label{ch:overview}

% Ethereum, taken as a whole, can be viewed as a transaction-based state machine: we begin with a genesis state and incrementally execute transactions to morph it into some current state. It is this current state which we accept as the canonical ``version'' of the world of Ethereum. The state can include such information as account balances, reputations, trust arrangements, data pertaining to information of the physical world; in short, anything that can currently be represented by a computer is admissible. Transactions thus represent a valid arc between two states; the `valid' part is important---there exist far more invalid state changes than valid state changes. Invalid state changes might, \eg, be things such as reducing an account balance without an equal and opposite increase elsewhere. A valid state transition is one which comes about through a transaction. Formally:
% \begin{equation}
% \linkdest{Upsilon_state_transition}\linkdest{Upsilon}\boldsymbol{\sigma}_{t+1} \equiv \Upsilon(\boldsymbol{\sigma}_{t}, T)
% \end{equation}

% where $\Upsilon$ is the Ethereum state transition function. In Ethereum, $\Upsilon$, together with $\boldsymbol{\sigma}$ are considerably more powerful than any existing comparable system; $\Upsilon$ allows components to carry out arbitrary computation, while $\boldsymbol{\sigma}$ allows components to store arbitrary state between transactions.

% Transactions are collated into blocks; blocks are chained together using a cryptographic hash as a means of reference. Blocks function as a journal, recording a series of transactions together with the previous block and an identifier for the final state (though do not store the final state itself---that would be far too big). They also punctuate the transaction series with incentives for nodes to \textit{mine}. This incentivisation takes place as a state-transition function, adding value to a nominated account.

% Mining is the process of dedicating effort (working) to bolster one series of transactions (a block) over any other potential competitor block. It is achieved thanks to a cryptographically secure proof. This scheme is known as a proof-of-work and is discussed in detail in section \ref{ch:pow}.

% Formally, we expand to:
% \begin{eqnarray}
  ブテリン [2013a]は、2013年11月末にこの研究のカーネルを初めて提案しました。現在では多くの点で進化していますが、チューリング完全言語と事実上無制限のトランザクション間保存能力を持つブロックチェーンの主要な機能は変わっていません。

  DworkとNaor[1992]は、計算の暗号学的証明の使用に関する最初の研究を提供しました。
  Dwork と Naor [1992]は、インターネット上で価値信号を伝送する手段として、暗号による計算支出の証明（「プルーフ・オブ・ワーク」）の使用に関する最初の研究を提供しました。この価値信号は、通貨としてではなく、スパム抑止メカニズムとして利用されたが、基本的なデータチャネルが強力な経済信号を伝送する可能性を決定的に示し、受信者が信頼に頼ることなく物理的な主張をすることを可能にするものであった。Back [2002]は、後に同じような系統のシステムを作成した。

  通貨を確保するための強力な経済シグナルとしてプルーフ・オブ・ワークを活用した最初の例は、Vishnumurthy ら [2003]によるものであった。この例では、トークンはピアツーピアのファイル取引を維持するために使用され、「消費者」が「供給者」に対してサービスに対するマイクロペイメントを行う能力を提供しました。プルーフ・オブ・ワークが提供するセキュリティ・モデル
  このプルーフ・オブ・ワークのセキュリティモデルは、電子署名と台帳によって強化され、履歴記録が破損しないように、また悪意のある行為者が支払いを偽装したり、サービス提供に対して不当に文句を言ったりできないようにするために利用されました。その5年後、Nakamoto [2008]は、このようなプルーフ・オブ・ワークで保護された、より広範囲なバリュー・トークンを発表した。

  このプロジェクトの成果であるビットコインは、世界的に広く採用された最初の分散型取引台帳となった。

  ビットコインの成功を受けて、他のプロジェクトが立ち上がりました。アルトコインは、プロトコルを変更することで、他の多くの通貨を導入しました。最もよく知られているのは、Sprankel [2013]が論じたLitecoinとPrimecoinです。

  Aron [2012]は、分散型名前解決システムを提供することを目的としたNamecoinプロジェクトについて論じています。

  その他のプロジェクトは、ビットコインのネットワークそのものを構築することを目的としており、ビットコインのシステム内にある大量の価値と、コンセンサスメカニズムにかかる膨大な計算量を利用しています。
  このようなプロジェクトもあります。

  Willett氏[2013]によって最初に提案されたMastercoinプロジェクトは、よりリッチなプロトコルを構築することを目的としています。
  コアプロトコルの補助的な部分を利用することで、ビットコインプロトコルの上に多くのハイレベルな機能を追加した、よりリッチなプロトコルを構築することを目的としています。Rosenfeld et al.

  [2012]によって提案されたColoured Coinsプロジェクトは、似たような、しかしより単純化された戦略を取り、ファンジョナルを破るために取引のルールを装飾しています。
  ビットコインの基本通貨の換金性をなくし、特別な「クロマウォレット」プロトコルを認識するソフトウェアを通じてトークンの作成と追跡を可能にするために、取引のルールを装飾しています。

  Boutellier and Heinzen [2014]によって議論されたRippleは、通貨交換のための「連合」システムを作ろうとし、事実上新しい金融決済システムを作ろうとしています。分散化の前提を捨てれば、高い効率化が可能であることを実証している。

  スマートコントラクトに関する初期の研究は、Szabo [1997]とMiller [1997]が行っている。1990年代には、アルゴリズムによる契約の強制が人間の協力関係において大きな力になり得ることが明らかになった。

  そのようなシステムを実現するための具体的なシステムは提案されていなかったが、その際、そのようなシステムによって法律の未来が大きく左右されることが提唱された。このような観点から、イーサリアムはそのような暗号法システムの一般的な実装と見なすことができるだろう。

  本稿で使用した用語の一覧は、付録 A を参照。
\boldsymbol{\sigma}_{t+1} & \equiv & \hyperlink{Pi}{\Pi}(\boldsymbol{\sigma}_{t}, B) \\
B & \equiv & (..., (T_0, T_1, ...), ...) \\
\Pi(\boldsymbol{\sigma}, B) & \equiv & \hyperlink{Omega}{\Omega}(B, \hyperlink{Upsilon}{\Upsilon}(\Upsilon(\boldsymbol{\sigma}, T_0), T_1) ...)
\end{eqnarray}
